RD design analysis

### 2024-05-04 analysis/RD design for density.Rmd
Add files via upload

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

@@

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1) # first using default clustering
```

@@

```{r}
h = 0.095
cutoff = 0.41
running_var = panel_data$nearest_store_distances

@@

par(mfrow=c(3,1))
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

>>>>

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
                   c = 0.2,
                   p = 1) # first using default clustering
```

@@

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
                   c = 0.41,
                   p = 1) # first using default clustering
```

@@

```{r}
h = 0.095
cutoff = 0.5
running_var = panel_data$density

@@

par(mfrow=c(3,1))
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$density, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$density, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$density, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```
